---
title: "geom_label"
author: "Ethel Ruan"
date: "2017-01-20"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#geom_label
`geom_label`(geom_text)/current/geom_text.html
**Textual annotations.**

##Usage
```
geom_label(mapping = NULL, data = NULL, stat = "identity", position = "identity", ..., parse = FALSE, nudge_x = 0, nudge_y = 0, label.padding = unit(0.25, "lines"), label.r = unit(0.15, "lines"), label.size = 0.25, na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)

geom_text(mapping = NULL, data = NULL, stat = "identity", position = "identity", ..., parse = FALSE, nudge_x = 0, nudge_y = 0, check_overlap = FALSE, na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)
```

##Description
`geom_text` adds text directly to the plot. 
`geom_label` draws a rectangle underneath the text, making it easier to read.

##Details
Note the the "width" and "height" of a text element are 0, so stacking and dodging text will not work by default, and axis limits are not automatically expanded to include all text. Obviously, labels do have height and width, but they are physical units, not data units. The amount of space they occupy on that plot is not constant in data units: when you resize a plot, labels stay the same size, but the size of the axes changes.

##Aesthetics
`geom_text` understands the following aesthetics (required aesthetics are in bold):
```
label
x
y
alpha
angle
colour
family
fontface
hjust
lineheight
size
vjust
```

##Examples
```{r}
library(ggplot2)
p <- ggplot(mtcars, aes(wt, mpg, label = rownames(mtcars)))

p + geom_point() +
  geom_text(
    size = 3,
    hjust = 0,
    nudge_x = 0.05,
    check_overlap = TRUE
  ) +
  geom_label(aes(fill = factor(cyl)), colour = "white", fontface = "bold") +
  geom_text(
    vjust = 0,
    nudge_y = 0.5,
    fille = "red",
    alpha = 0.5,
    angle = 45,
    aes(colour = factor(cyl), size = wt),
  ) +
  scale_radius(range = c(3, 6)) +
  geom_text(aes(label = paste(wt, "^(", cyl, ")", sep = "")), parse = TRUE) +
  annotate(
    "text",
    label = "plot mpg vs. wt",
    x = 2,
    y = 15,
    size = 8,
    colour = "blue"
  )
```
        