---
title: "geom_ribbon"
author: "Ethel Ruan"
date: "2017-01-20"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#geom_ribbon
`geom_ribbon`(geom_area) 
**Ribbons and area plots.**
         

##Usage
```
geom_ribbon(mapping = NULL, data = NULL, stat = "identity", position = "identity", ..., na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)

geom_area(mapping = NULL, data = NULL, stat = "identity", position = "stack", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE, ...)
```


##Description

For each continuous x value, `geom_interval` displays a y interval. `geom_area` is a special case of `geom_ribbon`, where the minimum of the range is fixed to 0.

##Details

An area plot is the continuous analog of a stacked bar chart (see geom_bar), and can be used to show how composition of the whole varies over the range of x. Choosing the order in which different components is stacked is very important, as it becomes increasing hard to see the individual pattern as you move up the stack.

##Aesthetics

`geom_ribbon` understands the following aesthetics (required aesthetics are in bold):
```
    x
    ymax
    ymin
    alpha
    colour
    fill
    linetype
    size
```
##Examples
```{r}
library(ggplot2)
# Generate data
huron <- data.frame(year = 1875:1972, level = as.vector(LakeHuron))
h <- ggplot(huron, aes(year))
# Add aesthetic mappings
h +
  geom_ribbon(aes(ymin = level - 1, ymax = level + 1), fill = "grey70") +
  geom_line(aes(y = level))
```

         