---
title: "geom_raster"
author: "Ethel Ruan"
date: "2017-01-20"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#geom_raster
`geom_raster`(geom_rect, geom_tile)
**Draw rectangles.**
          

##Usage
```
geom_raster(mapping = NULL, data = NULL, stat = "identity", position = "identity", ..., hjust = 0.5, vjust = 0.5, interpolate = FALSE, na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)

geom_rect(mapping = NULL, data = NULL, stat = "identity", position = "identity", ..., na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)

geom_tile(mapping = NULL, data = NULL, stat = "identity", position = "identity", ..., na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)
```
##Description

`geom_rect` and `geom_tile` do the same thing, but are parameterised differently. 
`geom_rect` uses the locations of the four corners (xmin, xmax, ymin and ymax). 
`geom_tile` uses the center of the tile and its size (x, y, width, height). 
`geom_raster` is a high performance special case for when all the tiles are the same size.

##Aesthetics

`geom_tile` understands the following aesthetics (required aesthetics are in bold):
```
    x
    y
    alpha
    colour
    fill
    linetype
    size
```
##Examples
```{r}
library(ggplot2)
 # The most common use for rectangles is to draw a surface. You always want
 # to use geom_raster here because it's so much faster, and produces
 # smaller output when saving to PDF
ggplot(faithfuld, aes(waiting, eruptions)) +
 geom_raster(aes(fill = density))

```
       
```{r}
 # Interpolation smooths the surface & is most helpful when rendering  s.
ggplot(faithfuld, aes(waiting, eruptions)) +
 geom_raster(aes(fill = density), interpolate = TRUE)
 ```
         
```{r}

 # If you want to draw arbitrary rectangles, use geom_tile() or geom_rect()
df <- data.frame(
  x = rep(c(2, 5, 7, 9, 12), 2),
  y = rep(c(1, 2), each = 5),
  z = factor(rep(1:5, each = 2)),
  w = rep(diff(c(0, 4, 6, 8, 10, 14)), 2)
)
ggplot(df, aes(x, y)) +
  geom_tile(aes(fill = z))
```
         
```{r}
ggplot(df, aes(x, y)) +
  geom_tile(aes(fill = z, width = w), colour = "grey50")
```
        

```{r}
ggplot(df, aes(xmin = x - w / 2, xmax = x + w / 2, ymin = y, ymax = y + 1)) +
  geom_rect(aes(fill = z, width = w), colour = "grey50")
```
      -13k  

```{r}
# Justification controls where the cells are anchored
df <- expand.grid(x = 0:5, y = 0:5)
df$z <- runif(nrow(df))
# default is compatible with geom_tile()
ggplot(df, aes(x, y, fill = z)) + geom_raster()


# zero padding
ggplot(df, aes(x, y, fill = z)) + geom_raster(hjust = 0, vjust = 0)
```
         

```{r}
# Inspired by the  -density plots of Ken Knoblauch
cars <- ggplot(mtcars, aes(mpg, factor(cyl)))
cars + stat_density(aes(fill = ..density..), geom = "raster", position = "identity")
```
       
