---
title: "geom_violin"
author: "Ethel Ruan"
date: "2017-01-20"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#geom_violin
`geom_violin`(stat_ydensity) 
**Violin plot.**
        

##Usage
```
geom_violin(mapping = NULL, data = NULL, stat = "ydensity", position = "dodge", ..., draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)

stat_ydensity(mapping = NULL, data = NULL, geom = "violin", position = "dodge", ..., bw = " ", adjust = 1, kernel = "gaussian", trim = TRUE, scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)
```
##Aesthetics

`geom_violin` understands the following aesthetics (required aesthetics are in bold):
```
    x
    y
    alpha
    colour
    fill
    linetype
    size
    weight
```
##Computed variables

density
    density estimate

scaled
    density estimate, scaled to maximum of 1

count
    density * number of points - probably useless for violin plots

violinwidth
    density scaled for the violin plot, according to area, counts or to a constant maximum width

n
    number of points

width
    width of violin bounding box

##References

Hintze, J. L., Nelson, R. D. (1998) Violin Plots: A Box Plot-Density Trace Synergism. The American Statistician 52, 181 

##Examples
```{r}
library(ggplot2)
library(ggplot2movies)
# Scales vs. coordinate transforms -------
if (require("ggplot2movies")) {
# Scale transformations occur before the density statistics are computed.
# Coordinate transformations occur afterwards.  Observe the effect on the
# number of outliers.
m <- ggplot(movies, aes(y = votes, x = rating, group = cut_width(rating, 0.5)))
m + geom_violin()
m + geom_violin() + scale_y_log10()
m + geom_violin() + coord_trans(y = "log10")
m + geom_violin() + scale_y_log10() + coord_trans(y = "log10")

# Violin plots with continuous x:
# Use the group aesthetic to group observations in violins
ggplot(movies, aes(year, budget)) + geom_violin()
ggplot(movies, aes(year, budget)) +
  geom_violin(aes(group = cut_width(year, 10)), scale = "width")
}

```
       

