---
title: "geom_path"
author: "Ethel Ruan"
date: "2017-01-20"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#geom_path
`geom_path`(geom_line, geom_step)
**Connect observations.**
          

##Usage
```
geom_path(mapping = NULL, data = NULL, stat = "identity", position = "identity", ..., lineend = "butt", linejoin = "round", linemitre = 1, arrow = NULL, na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)

geom_line(mapping = NULL, data = NULL, stat = "identity", position = "identity", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE, ...)

geom_step(mapping = NULL, data = NULL, stat = "identity", position = "identity", direction = "hv", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE, ...)
```

##Description
`geom_path()` connects the observations in the order in which they appear in the data. 
`geom_line()` connects them in order of the variable on the x axis.
`geom_step()` creates a stairstep plot, highlighting exactly when changes occur.

##Aesthetics
`geom_path` understands the following aesthetics (required aesthetics are in bold):

```
x
y
alpha
colour
linetype
size
```

##Examples
```{r}
library(ggplot2)
  ggplot(economics, aes(date, unemploy)) +
  geom_line(colour = "red",arrow = arrow(angle = 15, ends = "both", type = "closed")) +
  geom_path(
    aes(colour = as.numeric(date)),
    alpha = 0.5,
    size = 10,
    lineend = "round",
    linejoin = "mitre"
  ) 
  
```
        

```{r}
m <- ggplot(economics, aes(unemploy/pop, psavert))
m + geom_path(aes(colour = as.numeric(date))) + geom_step(alpha = 0.5,colour = "pink",linetype = 2)

```
         

```{r}
recent <- economics[economics$date > as.Date("2013-01-01"),]
ggplot(recent, aes(date, unemploy)) + geom_line() + geom_step(colour = "red")
```
         

```{r}
 # Setting line type vs colour/size
 # Line type needs to be applied to a line as a whole, so it can
 # not be used with colour or size that vary across a line
x <- seq(0.01, .99, length.out = 100)
df <- data.frame(
  x = rep(x, 2),
  y = c(qlogis(x), 2 * qlogis(x)),
  group = rep(c("a","b"),
  each = 100)
)
 ggplot(df, aes(x=x, y=y, group=group)) + geom_line(aes(colour = group), linetype = 2)
```
          