---
title: "geom_dotplot"
author: "Ethel Ruan"
date: "2017-01-20"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#geom_dotplot
`geom_dotplot` 
**Dot plot**
       

##Usage
```
geom_dotplot(mapping = NULL, data = NULL, position = "identity", ..., binwidth = NULL, binaxis = "x", method = "dotdensity", binpositions = "bygroup", stackdir = "up", stackratio = 1, dotsize = 1, stackgroups = FALSE, origin = NULL, right = TRUE, width = 0.9, drop = FALSE, na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)
```

##Description
In a dot plot, the width of a dot corresponds to the bin width (or maximum width, depending on the binning algorithm), and dots are stacked, with each dot representing one observation.

##Details
With dot-density binning, the bin positions are determined by the data and `binwidth`, which is the maximum width of each bin. See Wilkinson (1999) for details on the dot-density binning algorithm.

With histodot binning, the bins have fixed positions and fixed widths, much like a histogram.

When binning along the x axis and stacking along the y axis, the numbers on y axis are not meaningful, due to technical limitations of  . You can hide the y axis, as in one of the examples, or manually scale it to match the number of dots.

##Aesthetics
`geom_dotplot` understands the following aesthetics (required aesthetics are in bold):
```
    x
    y
    alpha
    colour
    fill
```
##Computed variables

x
    center of each bin, if binaxis is "x"

y
    center of each bin, if binaxis is "x"

binwidth
    max width of each bin if method is "dotdensity"; width of each bin if method is "histodot"

count
    number of points in bin

ncount
    count, scaled to maximum of 1

density
    density of points in bin, scaled to integrate to 1, if method is "histodot"

ndensity
    density, scaled to maximum of 1, if method is "histodot"

##References
Wilkinson, L. (1999) Dot plots. The American Statistician, 53(3), 276 

##Examples
```{r}
library(ggplot2)
#`stat_bindot()` using `bins = 30`. Pick better value with `binwidth`.
ggplot(mtcars, aes(x = mpg)) + 
  geom_dotplot() +
  geom_dotplot(binwidth = 1.5,fill = "red",alpha = 0.1) +
  #use fixed-width bins
  geom_dotplot(method="histodot", binwidth = 1.5,fill= "blue",alpha = 0.5)  

```
     
ggplot(mtcars, aes(x = mpg)) + geom_dotplot(binwidth = 1.5)

```{r}
ggplot(mtcars, aes(x = mpg)) + 
  geom_dotplot(binwidth = 1.5, stackdir = "center",fill = "red",alpha = 0.1) +
  geom_dotplot(binwidth = 1.5, stackdir = "centerwhole",fill = "blue", alpha = 0.1)
```
        

```{r}
  # y axis isn't really meaningful, so hide it
  ggplot(mtcars, aes(x = mpg)) + geom_dotplot(binwidth = 1.5,alpha= 0.1) +
  scale_y_continuous(NULL, breaks = NULL) +
  # Overlap dots vertically
  geom_dotplot(binwidth = 1.5, stackratio = .7,fill = "blue",alpha = 0.1) +
  # Expand dot diameter
  geom_dotplot(binwidth = 1.5, dotsize = 1.25,fill = "red",alpha= 0.1)
```
       

```{r}
# Examples with stacking along y axis instead of x
ggplot(mtcars, aes(x = 1, y = mpg)) +
  geom_dotplot(binaxis = "y", stackdir = "center")
```
`stat_bindot()` using `bins = 30`. Pick better value with `binwidth`.
       

```{r}
ggplot(mtcars, aes(x = factor(cyl), y = mpg)) +
  geom_dotplot(binaxis = "y", stackdir = "center")
```

`stat_bindot()` using `bins = 30`. Pick better value with `binwidth`.
       

```{r}
ggplot(mtcars, aes(x = factor(vs), fill = factor(cyl), y = mpg)) +
  geom_dotplot(binaxis = "y", stackdir = "center", position = "dodge")
```
        

```{r}
# binpositions="all" ensures that the bins are aligned between groups
ggplot(mtcars, aes(x = factor(am), y = mpg)) +
  geom_dotplot(binaxis = "y", stackdir = "center", binpositions="all")

# `stat_bindot()` using `bins = 30`. Pick better value with `binwidth`.
```
           

```{r}
# Stacking multiple groups, with different fill
ggplot(mtcars, aes(x = mpg, fill = factor(cyl))) +
  geom_dotplot(stackgroups = TRUE, binwidth = 1, binpositions = "all")
```
        

```{r}
# Stacking multiple groups, with different fill
ggplot(mtcars, aes(x = mpg, fill = factor(cyl))) +
  geom_dotplot(stackgroups = TRUE, binwidth = 1, binpositions = "all")
```
        

```{r}
ggplot(mtcars, aes(x = 1, y = mpg, fill = factor(cyl))) +
  geom_dotplot(binaxis = "y", stackgroups = TRUE, binwidth = 1, method = "histodot")
```
         
