---
title: "geom_density_2d"
author: "Ethel Ruan"
date: "2017-01-19"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#geom_density_2d
`geom_density_2d` (geom_ d, stat_ d, stat_density_2d)
**Contours from a 2d density estimate.**
        

##Usage
```
geom_density_2d(mapping = NULL, data = NULL, stat = " d", position = "identity", ..., lineend = "butt", linejoin = "round", linemitre = 1, na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)

stat_density_2d(mapping = NULL, data = NULL, geom = "density_2d", position = "identity", ..., contour = TRUE, n = 100, h = NULL, na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)
```

##Description
Perform a 2D kernel density estimation using  d and display the results with contours. This can be useful for dealing with overplotting.

##Aesthetics
`geom_density_2d` understands the following aesthetics (required aesthetics are in bold):
```
    x
    y
    alpha
    colour
    linetype
    size
```
##Computed variables

Same as stat_contour

##Examples
```{r}
library(ggplot2)
m <- ggplot(faithful, aes(x = eruptions, y = waiting)) +
 geom_point() +
 xlim(0.5, 6) +
 ylim(40, 110)
m + geom_density_2d()
```
         

```{r}
m + stat_density_2d(aes(fill = ..level..), geom = "polygon")
```
        

```{r}
set.seed(4393)
dsmall <- diamonds[sample(nrow(diamonds), 1000), ]
d <- ggplot(dsmall, aes(x, y))
# If you map an aesthetic to a categorical variable, you will get a
# set of contours for each value of that variable
d + geom_density_2d(aes(colour = cut))
```
          

```{r}
# If we turn contouring off, we can use use geoms like tiles:
d + stat_density_2d(geom = "raster", aes(fill = ..density..), contour = FALSE)
```
          

```{r}
# Or points:
d + stat_density_2d(geom = "point", aes(size = ..density..), n = 20, contour = FALSE)
```
        