---
title: "geom_bar"
author: "Ethel Ruan"
date: "2017-01-19"
output: 
  html_document: 
    keep_md: yes
---

```r
library(ggplot2)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



**Bars, rectangles with bases on x-axis**


##Usage
```
geom_bar(mapping = NULL, data = NULL, stat = "count", position = "stack", ..., width = NULL, binwidth = NULL, na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)

stat_count(mapping = NULL, data = NULL, geom = "bar", position = "stack", ..., width = NULL, na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)
```

##Examples

```{r}
reorder_size <- function(x) {
  factor(x, levels = names(sort(table(x))))
}

ggplot(mpg, aes(reorder_size(class))) + geom_bar(fill = "blue",alpha = 0.1)

ggplot(mpg, aes(class)) +
  geom_bar(aes(fill = drv), position = "dodge") +
  geom_bar(aes(weight = displ),alpha = 0.1,fill = "pink")

df <- data.frame(trt = c("a", "b", "c"), outcome = c(2.3, 1.9, 3.2))
ggplot(df, aes(trt, outcome)) +
  geom_bar(stat = "identity",fill = "pink") +
  geom_point(colour = "red")

df <- data.frame(x = rep(c(2.9, 3.1, 4.5), c(5, 10, 4)))
ggplot(df, aes(x)) + geom_bar(fill = "pink") + geom_histogram(binwidth = 0.5,alpha = 0.2) 
```


##See also

**geom_histogram** for continuous data, 

`position_dodge` for creating side-by-side barcharts. 

`stat_bin`, which bins data in ranges and counts the cases in each range.

It differs from `stat_count`, which counts the number of cases at each x position (without binning into ranges). 

`stat_bin` requires continuous x data, whereas stat_count can be used for both discrete and continuous x data.
