---
title: "geom_smooth"
author: "Ethel Ruan"
date: "2017-01-20"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#geom_smooth
`geom_smooth`(stat_smooth) 
**Add a smoothed conditional mean.**
        

##Usage
```
geom_smooth(mapping = NULL, data = NULL, stat = "smooth", position = "identity", ..., method = "auto", formula = y ~ x, se = TRUE, na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)

stat_smooth(mapping = NULL, data = NULL, geom = "smooth", position = "identity", ..., method = "auto", formula = y ~ x, se = TRUE, n = 80, span = 0.75, fullrange = FALSE, level = 0.95, method.args = list(), na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)
```


##Description

Aids the eye in seeing patterns in the presence of overplotting. `geom_smooth` and `stat_smooth` are effectively aliases: they both use the same arguments. Use `geom_smooth `unless you want to display the results with **a non-standard geom.**

##Details

Calculation is performed by the (currently undocumented) predictdf generic and its methods. For most methods the standard error bounds are computed using the predict method - the exceptions are loess which uses a t-based approximation, and glm where the normal confidence interval is constructed on the link scale, and then back-transformed to the response scale.

##Aesthetics

`geom_smooth` understands the following aesthetics (required aesthetics are in bold):
```
    x
    y
    alpha
    colour
    fill
    linetype
    size
    weight
```
##Computed variables

y
    predicted value

ymin
    lower pointwise confidence interval around the mean

ymax
    upper pointwise confidence interval around the mean

se
    standard error

##Examples
```{r}
library(ggplot2)

# Use span to control the "wiggliness" of the default loess smoother
# The span is the fraction of points used to fit each local regression:
# small numbers make a wigglier curve, larger numbers make a smoother curve.
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  geom_smooth(span = 0.3) +
  geom_smooth(method = "lm", se = FALSE,colour = "red") +
  geom_smooth(method = "lm", formula = y ~ splines::bs(x, 3), se = FALSE,colour = "blue") 
 ```
         

```{r}
# Smoothes are automatically fit to each group (defined by categorical
# aesthetics or the group aesthetic) and for each facet

ggplot(mpg, aes(displ, hwy, colour = class)) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm")
```
        

```{r}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  geom_smooth(span = 0.8) +
  facet_wrap(~drv)
```
          

```{r}
binomial_smooth <- function(...) {
  geom_smooth(method = "glm", method.args = list(family = "binomial"), ...)
}
# To fit a logistic regression, you need to coerce the values to
# a numeric vector lying between 0 and 1.
ggplot(rpart::kyphosis, aes(Age, as.numeric(Kyphosis) - 1)) +
  geom_jitter(height = 0.05) +
  binomial_smooth() +
  binomial_smooth(formula = y ~ splines::ns(x, 2),colour = "red")
  
```
       
