---
title: "geom_freqploy"
author: "Ethel Ruan"
date: "2017-01-20"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#geom_freqploy
`geom_freqpoly` (geom_histogram, stat_bin)
**Histograms and frequency polygons.**
         

##Usage
```
geom_freqpoly(mapping = NULL, data = NULL, stat = "bin", position = "identity", ..., na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)

geom_histogram(mapping = NULL, data = NULL, stat = "bin", position = "stack", ..., binwidth = NULL, bins = NULL, na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)

stat_bin(mapping = NULL, data = NULL, geom = "bar", position = "stack", ..., binwidth = NULL, bins = NULL, center = NULL, boundary = NULL, closed = c("right", "left"), pad = FALSE, na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)
```

##Description
Display a 1d distribution by dividing into bins and counting the number of observations in each bin. Histograms use bars; frequency polygons use lines.
`stat_bin` is suitable only for continuous x data. If your x data is discrete, you probably want to use stat_count.

##Details
By default, `stat_bin` uses **30 bins** - this is not a good default, but the idea is to get you experimenting with different binwidths. You may need to look at a few to uncover the full story behind your data.

##Aesthetics
`geom_histogram` uses the same aesthetics as `geom_bar`; `geom_freqpoly` uses the same aesthetics as `geom_line`.

##Computed variables

count
    number of points in bin

density
    density of points in bin, scaled to integrate to 1

ncount
    count, scaled to maximum of 1

ndensity
    density, scaled to maximum of 1

##Examples
```{r}
library(ggplot2)
#`stat_bin()` using `bins = 30`. Pick better value with `binwidth`.
ggplot(diamonds, aes(carat)) +
  geom_histogram(alpha = 0.1) +
  geom_histogram(binwidth = 0.01,fill = "red",alpha= 0.1) +
  geom_histogram(bins = 200,fill = "blue",alpha = 0.1)
```
       

```{r}
# Rather than stacking histograms, it's easier to compare frequency
# polygons
ggplot(diamonds, aes(price, fill = cut)) +
  geom_histogram(binwidth = 500)
```
         

```{r}
ggplot(diamonds, aes(price, colour = cut)) +
  geom_freqpoly(binwidth = 500)
```
    
```{r}
# To make it easier to compare distributions with very different counts,
# put density on the y axis instead of the default count
ggplot(diamonds, aes(price, ..density.., colour = cut)) +
  geom_freqpoly(binwidth = 500)
```
         


         