---
title: "ggvis Cookbook"
author: "Ethel Ruan"
date: "2017-02-05"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following examples show you how to create a selection of common graphics with ggvis. First, load ggvis and dplyr:

```{r}
library(ggvis)
library(dplyr)
```

##Scatterplots

We’ll use the built-in `mtcars` data set, and look at two columns of interest, `mpg` ,and `wt`:
```{r}
# The first few rows of mtcars
head(mtcars)
```

```{r}
mtcars %>% ggvis(~wt, ~mpg) %>% layer_points()
```
                   

Smaller points, a different shape, a different outline (stroke) color, and empty fill:

```{r}
mtcars %>% 
  ggvis(~wt, ~mpg) %>% 
  layer_points(size := 25, shape := "diamond", stroke := "red", fill := NA)

```


# Regression lines

Adding a smooth line

```{r}
mtcars %>% 
  ggvis(~wt, ~mpg) %>% 
  layer_points() %>% 
  layer_smooths()
```


With a linear model, and 95% confidence interval for the model:

```{r}
mtcars %>% 
  ggvis(~wt, ~mpg) %>% 
  layer_points() %>% 
  layer_model_predictions(model = "lm", se = TRUE)
```


#Scatter plots with grouping

Coloring points by a variable:
```{r}
mtcars %>% 
  ggvis(~wt, ~mpg) %>% 
  layer_points(fill = ~factor(cyl))
  
  #or
   mtcars %>% 
    ggvis(~wt, ~mpg,fill = ~factor(cyl)) %>% 
    layer_points()
```


Coloring points, and adding a smoother for each group. 
The grouping variable (which is applied before the transform_smooth is calculated) must be specified with `group_by()`:

```{r}
mtcars %>% 
  ggvis(~wt, ~mpg, fill = ~factor(cyl)) %>% 
  layer_points() %>% 
  group_by(cyl) %>% 
  layer_model_predictions(model = "lm")
```

or
```
mtcars %>% 
     ggvis(~wt, ~mpg ) %>% 
     layer_points(fill = ~factor(cyl)) %>% 
     group_by(cyl) %>% 
    layer_model_predictions(model = "lm")
    
```

## Bar graphs

We’ll use the built-in pressure data set for these examples:
```{r}
  # The first few rows

head(pressure)
```


When the variable on the x axis is continuous (e.g., numeric or date-time):
```{r}
pressure %>% 
  ggvis(~temperature, ~pressure) %>% 
  layer_bars()
```

It’s possible to specify the `width` of the bars:

```{r}
pressure %>% 
  ggvis(~temperature, ~pressure) %>% 
  layer_bars(width = 10)
```


When the variable on the x axis is categorical (e.g., factor or character):

```{r}

  #First, modify the pressure data set so that the x variable is a factor

pressur <- pressure %>% mutate(temperature = factor(temperature))
pressure


pressur %>% ggvis(~temperature, ~pressure) %>% 
  layer_bars()
```


## Line graphs

```{r}
pressure %>% ggvis(~temperature, ~pressure) %>% layer_lines()
```


## Lines with points:
```{r}
pressure %>% ggvis(~temperature, ~pressure) %>% 
  layer_points() %>% 
  layer_lines()
```


## Histograms
We’ll use the built-in **faithful** data set for these examples:

```{r}
  # The first few rows
  
 head(faithful)

```

## Basic histogram:
```{r}
faithful %>% ggvis(~eruptions) %>% layer_histograms()
```

```{r}
faithful %>% ggvis(~waiting) %>% layer_histograms()
```


The bin selection can be controled by specifying `width` and at most one of `center` or `boundary` of one of the bins. boundary and center may be outside the range of the data.

```{r}
faithful %>% ggvis(~eruptions) %>% layer_histograms(width=0.5, boundary=0)
```


```{r}
faithful %>% ggvis(~eruptions) %>% layer_histograms
```


```{r}
 faithful %>% ggvis(~eruptions) %>% layer_histograms(width=0.5, center=0)
```

Modify the fill color and bin width, and add titles for the axes, since the automatic titles aren’t very informative:
```{r}
faithful %>% ggvis(~eruptions, fill := "#ffdc") %>% 
  layer_histograms(width = 0.25)
```

By default, when the number of integer values is small, bins will be centered at integers and have a width of 1:
```{r}
# name axis x & y
cocaine %>% ggvis(~month, fill := "#ffdc") %>% 
  layer_histograms() %>% 
  add_axis("x", title = "month") %>% 
  add_axis("y", title = "count")
# range / 22
```


This can be forced with
```{r}
cocaine %>% ggvis(~month, fill := "#ffdc") %>% 
layer_histograms(width = 1, center = 0) %>% 
add_axis("x", title = "month") %>% 
add_axis("y", title = "count")
```


## Box plots
```{r}
mtcars %>% ggvis(~factor(cyl), ~mpg) %>% layer_boxplots()
```