---
title: "regex_examples"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Regular Expression Pattern

```{r}
text <- c("123456789ca@b.com a@qq.com", "123acb@qq.com")

# "?:" means do not capture ".com""
rex <- "([a-z]+)@([acb]|qq)+.(?:com)"

```

##Pattern Matching and Replacement
###regexpr 
search for matches to argument pattern within each element of a character vector
```{r}

#capture only the first qualified token in each vector
regexpr(rex,c("123456789ca@b.com a@qq.com", "123acb@qq.com"))
```

###gregexpr 
```{r}

#capture all the qualified tokens
gregexpr(rex,c("123456789ca@b.com a@qq.com", "123acb@qq.com")) 

```

###regmatches
```{r}

#extract or replace matched substrings
regmatches(c("123456789ca@b.com a@qq.com", "123acb@qq.com"), gregexpr(rex, c("123456789ca@b.com a@qq.com", "123acb@qq.com")))

```

###regexec
```{r}

#extract the exact matched parts of patten in the text
regexec(rex,c("123456789ca@b.com a@qq.com", "123acb@qq.com")) 

```


##gregexpr_matches 
##regexec_matches

```{r}

gregexpr_matches <- function(pattern, text){ regmatches(text, gregexpr(pattern, text))}
regexec_matches <- function(pattern, text){ regmatches(text, regexec(pattern, text))}

#split the functions and analyze them
gregexpr(rex, text)
a0 <- regmatches(text, gregexpr(rex, text))
regexec(rex, a0[[1]])
regmatches(a0[[1]], regexec(rex,a0[[1]]))

```

###gregexpr_matches 
```{r}
gregexpr_matches(rex, text)

```

###regexec_match vector1 
```{r}
a1<-gregexpr_matches(rex, text)[[1]]
a1
regexec_matches(rex, a1)

```

###regexec_match vector2
```{r}

a2<-gregexpr_matches(rex, text)[[2]]
a2 
regexec_matches(rex,a2)
```

##substring str
```{r}

res <- gregexpr(rex,text)
res

b1<- res[[1]][1]
b1

b2<- attr(res[[1]], "match.length")[1]
b2

```

###substring vector1-1
```{r}
text

substring(text[1], b1, b1+b2-1)

substr(text[1], b1, b1+b2-1)

```

###substring vector1-2
```{r}
b3 <- res[[1]][2]
b3
b4 <- attr(res[[1]],"match.length")[2]
b4
substring(text[1], b3, b3+b4-1)

substr(text[1], b3, b3+b4-1)
```

##substring vector2
```{r}
substring(text[2], res[[2]][1], res[[2]][1]+attr(res[[2]], "match.length")[1])

regmatches
a3 <- substring(text[2], res[[2]][1], res[[2]][1]+attr(res[[2]], "match.length")[1])
regmatches(a3,regexec(rex,a3))

```

```{r}

 sub("[a-z]{3,5}", 123, c("abcde123abc"))

 gsub("[a-z]{3,5}", 123, c("abcde123abc"))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
